From Object Classification to Naming:\\ Modeling Entry-level Names for Real-world Objects

### 2019-12-10 papers/ACL2020/experiments.tex
pass over sect 4 finished

% and furthermore report results on the test instances where the two names differ (block VG$\neq$MN). 
%Note that the VG names were derived on the basis of a few annotations per object only, and, as shown in Section~\ref{sect:mn_analysis}, even ``just'' $10$ or $20$ names sufficiently likely yield an entry-level name for only $68\%$ or $78\%$ instances, respectively.  
%We therefore consider an object's VG name less likely to represent the entry-level name than its MN name. 
% \gbt{add motivation for the latter, and make sure we address this when we discuss results; else, remove.}. 
%\cs{Left as items for the sake of a better overview for now}
\begin{table}[t]
	\centering
	\small
	\begin{tabular}{@{~}l@{~}|@{~}c@{~}|cc@{~}}
		\toprule
		&  & \multicolumn{2}{c}{GTtest} \\
		Model$_{\text{Vocab}}$ &  GTtrain &  VG & MN  \\ 
		\midrule
		FRCNN$_{\text{MN442}}$ & VG &  65.4 &      71.2   \\
		FRCNN$_{\text{VG1600}}$ & VG &    67.3 &      74.5 \\
		\midrule \midrule
		\multicolumn{4}{c}{Classifiers: Transfer learning on MN}\\
		Features$_{\text{Vocab}}$ &   \\
		\midrule 
		FRCNN$_{\text{VG1600}}$$_{\text{-VGMN}}$ & MN &    70.8 &      80.6  \\ 
		\midrule
		%ResNet$_{\text{VGMN}}$ & MN  & 60.9 &  68.6   \\

@@

A pervasive trend is that all models perform better 
at predicting the entry-level name (MN) than the VG name (VG), regardless of which vocabulary (Vocab) and which ground-truth (GTtrain) they are trained on.  
Note that the VG names were derived on the basis of a few annotations per object only, and, as shown in Section~\ref{sect:mn_analysis}, even ``just'' $10$ or $20$ names sufficiently likely yield an entry-level name for only $68\%$ or $78\%$ instances, respectively. 
The results therefore indicate that the even the FRCNN detection models do learn entry-level naming, with an accuracy of up to~$74.5$\%.

 The overall best model is FRCNN$_\text{VG1600}$$_\text{-VGMN}$ (the Vanilla classifier with FRCNN$_\text{VG1600}$ features, trained on the \mn). 
The classifiers using ResNet features are the least effective, but considering that they were trained on a fraction of FRCNN's training size using a simple Vanilla classifier, in contrast to a fully-fledged CNN architecture of the FRCNN object detectors, the drop in effectiveness on entry-level naming (column MN, GTtrain MN) is decently low. This confirms what we observed on the FRCNN results. 
In sum, we find that models learn entry-level naming when being trained on \arbitrary naming data, obtaining better results on entry-level prediction than VG name prediction for the same instances, and benefit from being trained on entry-levels using transfer learning. Comparing the target vocabulary, MN442 and VG1600/VGMN, we see that the restriction on a smaller, but empirically derived vocabulary of entry-level names only, is not beneficial, with all MN442 models being worse or comparable to VGMN/VG100.

@@

%To date, little research has been done on how to finetune and calibrate the \textit{vocabulary} of object detection and classification models from Computer Vision, for purposes of \lv.
As Section~\ref{sec:manynames} showed, object naming is a linguistically complex phenomenon which involves a lot of variation and potential errors, besides a fair amount of agreement.
Hence, it is striking that even models that are trained on (a lot of) \arbitrary names capture entry-level naming to a good extent.
However, our results also suggest that current \textit{evaluation} methods might not be very reliable when applied on \arbitrary names, probably punishing models for `errors' that actually constitute plausible alternatives.
The next section elaborates on this and proposes a more fair assessment of naming quality achieved by the different models.

>>>>

% and furthermore report results on the test instances where the two names differ (block VG$\neq$MN). 
%Note that the VG names were derived on the basis of a few annotations per object only, and, as shown in Section~\ref{sect:mn_analysis}, even ``just'' $10$ or $20$ names sufficiently likely yield an entry-level name for only $68\%$ or $78\%$ instances, respectively.  
%We therefore consider an object's VG name less likely to represent the entry-level name than its MN name. 
% \gbt{add motivation for the latter, and make sure we address this when we discuss results; else, remove.}. 
%\cs{Left as items for the sake of a better overview for now}
\begin{table}[t]
	\centering
	\small
	\begin{tabular}{@{~}l@{~}|@{~}c@{~}|cc@{~}}
		\toprule
		&  & \multicolumn{2}{c}{GTtest} \\
		Model$_{\text{Vocab}}$ &  GTtrain &  VG & MN  \\ 
		\midrule
		FRCNN$_{\text{MN442}}$ & VG &  65.4 &      71.2   \\
		FRCNN$_{\text{VG1600}}$ & VG &    67.3 &      {\bf 74.5} \\
		\midrule \midrule
		\multicolumn{4}{c}{Classifiers: Transfer learning on MN}\\
		Features$_{\text{Vocab}}$ &   \\
		\midrule 
		FRCNN$_{\text{VG1600}}$$_{\text{-VGMN}}$ & MN &    {\bf 70.8} &      {\bf 80.6}  \\ 
		\midrule
		%ResNet$_{\text{VGMN}}$ & MN  & 60.9 &  68.6   \\

@@

A pervasive trend is that all models perform better 
at predicting the entry-level name (MN) than the VG name (VG), regardless of which vocabulary (Vocab) and which ground-truth (GTtrain) they are trained on. 
Note that the VG names were derived on the basis of 1-2 annotations per object, which, as shown in Section~\ref{sect:mn_analysis}, is not enough to robustly estimate entry-level names.
%even ``just'' $10$ or $20$ names sufficiently likely yield an entry-level name for only $68\%$ or $78\%$ instances, respectively. 
The results therefore indicate that, even when not trained to do so (FRCNN$_{\text{VG1600}}$), models tend to predict entry-level names.
This is likely because entry-level names better reflect generalizations across objects.
% the FRCNN detection models do learn entry-level naming, with an accuracy of up to~$74.5$\%.

The overall best model is FRCNN$_\text{VG1600}$$_\text{-VGMN}$ (the transfer learning classifier with FRCNN$_\text{VG1600}$ features, trained on the \mn).
Fine-tuning on entry-level names also helps in the original task of predicting VG names, as FRCNN$_\text{VG1600}$$_\text{-VGMN}$ also improves in the VG evaluation (70.8\% accuracy, vs.\ \ 67.3\% without fine-tuning).
As expected, the classifiers using ResNet features obtain the worst results, but are still remarkably effective considering that they were trained on a fraction of FRCNN's training size using a simple transfer learning classifier.
%, in contrast to the fully-fledged CNN architecture of the FRCNN object detectors, the drop in effectiveness on entry-level naming (column MN, GTtrain MN) is decently low. 
%This confirms what we observed on the FRCNN results.

In sum, we find that models learn entry-level naming even when being trained on \arbitrary naming data, obtaining better results on entry-level prediction than VG name prediction for the same instances, and that they benefit from transfer learning with entry-level names. Instead, restricting the training vocabulary to entry-level names is not effective (all MN422 models are worse or comparable to VGMN/VG1600 models).
% Comparing the target vocabulary, MN442 and VG1600/VGMN, we see that the restriction on a smaller, but empirically derived vocabulary of entry-level names only, is not beneficial, with all MN442 models being worse or comparable to VGMN/VG100.

@@

%To date, little research has been done on how to finetune and calibrate the \textit{vocabulary} of object detection and classification models from Computer Vision, for purposes of \lv.
As Section~\ref{sec:manynames} showed, object naming is a linguistically complex phenomenon which exhibits a fair amount of agreement and also variation and potential errors.
Hence, it is striking that even models that are trained on \arbitrary names capture entry-level naming to a good extent.
However, our results also suggest that current \textit{evaluation} methods might not be very reliable when applied on \arbitrary names, probably punishing models for `errors' that actually constitute plausible alternatives.
The next section elaborates on this and proposes a fairer assessment of naming quality.
